### 2022-01-20 paper.tex
some references

\documentclass[12pt,titlepage,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{babel}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyphenat}
\usepackage{caption}

@@

\pagebreak
\section{Semantic Decoding}
Speech recogniser module of SLU translates speech into text and outputs a list of possible user utterances along with their probabilities (Figure \ref{fig:several}).

@@

can be translated into the sequence of tags: 
\begin{center}
    ["O", "O", "O", "O", "O", "B-fromloc.city\_name", "O", "B-toloc.city\_name", "B-round\_trip", "I-round\_trip", "B-departure\_date"]
\end{center}
\begin{figure}[!h]
    \centering
    \includegraphics[width=0.91\linewidth]{training-2-2.png}
    \caption{}
    \label{fig:semantic-decoding-seq2seq}
\end{figure}

Model predicting a sequence of tags can be a simple RNN with two heads --- one for predicting the tags and another for predicting intent or conditional random fields (CRF) instead (Figure \ref{fig:semantic-decoding-seq2seq}).

@@

\pagebreak
\begin{thebibliography}{ccccc}
\addcontentsline{toc}{section}{Literatur}

%So kann eine eine Monographie zitieren:
\bibitem{Arbarello et al 1985}
E.\ Arbarello, M.\ Cornalba, P.\ Griffiths, J.\ Harris:
Geometry of algebraic curves. I. 
Springer, New York, 1985.

%So kann man eine Originalarbeit zitieren:
\bibitem{Shepherd-Barron 1997}
N.\ Shepherd-Barron:
Fano threefolds in positive characteristic.
Compositio Math.\  105  (1997),  237--265.

\end{thebibliography}
\end{document}

>>>>

\documentclass[12pt,titlepage,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyphenat}
\usepackage{caption}
\usepackage[numbers]{natbib}

@@

\pagebreak
\section{Semantic Decoding}
Speech recogniser module of SLU translates speech into text and outputs a list of possible user utterances along with their probabilities using a hidden markov model (HMM)\cite{HMM} (Figure \ref{fig:several}).

@@

can be translated into the sequence of tags: 
\begin{center}
    ["O", "O", "O", "O", "O", "B-fromloc.city\_name", "O", "B-toloc.city\_name", "B-round\_trip", "I-round\_trip", "B-departure\_date"]
\end{center}
Using recurrent neural networks for slot filling in spoken language understanding.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.91\linewidth]{training-2-2.png}
    \caption{}
    \label{fig:semantic-decoding-seq2seq}
\end{figure}

Semantic parsing using word confusion networks with conditional random fields.

Model predicting a sequence of tags can be a simple RNN \cite{SemanticFilling} with two heads --- one for predicting the tags and another for predicting intent or conditional random fields (CRF) \cite{CRF} instead (Figure \ref{fig:semantic-decoding-seq2seq}).

@@

\bibliography{refs} 
\bibliographystyle{plainnat}

\end{document}
